Transition from forest to agriculture in the Brazilian Amazon from 1985 to 2021

### 2022-11-16 manuscript/manuscript.Rmd
Improve and expand introduction. Add todo paragraphs in the results.

In the last decades, the Amazon biome have been submitted to strong changes, the advance of agricultural areas over native forests is shaping a new landscape in the region.
The most common pattern of transitions from natural forest formations to agriculture sites, is the initial process of deforestation, followed by the establishment of pasture, where extensive livestock production takes place, until its replacement to agricultural activities.
This process can take several decades to be accomplished, or even less than one year, in which it may be considered as a direct transition from forest to agriculture.

@@

@@

>>>>

Brazil policies since the 1960s were focused on the expansion of the frontier in the Amazon, specially focused in economic income and land security [@Carvalho2002; @Mcdonald2003].
Such development model led to the construction of thousands of kilometers of roads, and the settlement of large scale livestock farms [@Carvalho2002].
This period was marked with high rates of deforestation of mature forests [@Fearnside2005].
At the same time, cattle and soybean productions started to move to the north direction in the Brazilian territory, in which soybeans cultivation areas followed cattle ranches expansion over the Amazon forest [@Simon2005].
This pattern of extensive livestock occupation after deforestation, followed by the establishment of annual crops is very characteristics in the Amazon biome, and persists nowadays.
This process can take several decades to be accomplished, or even less than one year, in which it may be considered as a direct transition from forest to agriculture.

@@

TODO: Talk about the Avança Brasil plan [@Carvalho2002].

@@

TODO: Talk about the percentage of each agriculture type in the total transitions.
And show numbers about what happens 5 years after transitions for each crop type.

### 2022-11-16 manuscript/manuscript.tex
Improve and expand introduction. Add todo paragraphs in the results.

In the last decades, the Amazon biome have been submitted to strong changes, the advance of agricultural areas over native forests is shaping a new landscape in the region.
The most common pattern of transitions from natural forest formations to agriculture sites, is the initial process of deforestation, followed by the establishment of pasture, where extensive livestock production takes place, until its replacement to agricultural activities.
This process can take several decades to be accomplished, or even less than one year, in which it may be considered as a direct transition from forest to agriculture.

@@

>>>>

Brazil policies since the 1960s were focused on the expansion of the frontier in the Amazon, specially focused in economic income and land security \citep{Carvalho2002, Mcdonald2003}.
Such development model led to the construction of thousands of kilometers of roads, and the settlement of large scale livestock farms \citep{Carvalho2002}.
This period was marked with high rates of deforestation of mature forests \citep{Fearnside2005}.
At the same time, cattle and soybean productions started to move to the north direction in the Brazilian territory, in which soybeans cultivation areas followed cattle ranches expansion over the Amazon forest \citep{Simon2005}.
This pattern of extensive livestock occupation after deforestation, followed by the establishment of annual crops is very characteristics in the Amazon biome, and persists nowadays.
This process can take several decades to be accomplished, or even less than one year, in which it may be considered as a direct transition from forest to agriculture.

@@

TODO: Talk about the Avança Brasil plan \citep{Carvalho2002}.
